---
title: "Gourp 1 Assignment 6 Final"
author: "Group 1"
date: "12/14/2020"
output: html_document
---
Set-up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Libraries
```{r}
library(tidyverse) #to clean and prep data
library(tidymodels) # to access some of the tidy model tools
library(janitor) # to clean data
library(googledrive)#to get files from Google drive
library(broom)#to extract the PCs and Clusters
```


#Task II: K-mean

Downloading files - This sections should only be used when downloading files for the first time or downloading new files.
```{r}
#using google drive to download files from Google Drive
#folder_url <- "https://drive.google.com/drive/folders/1am3wIQPXFvvFAmsJG2m85HLl0G63rJE4?usp=sharing" #This is the Googledrive folder with files
#folder <- drive_get(as_id(folder_url))
#csv_files <- drive_ls(folder, type = "csv")
#walk(csv_files$id, ~ drive_download(as_id(.x), overwrite = TRUE))
```

##Combining the files
```{r}
sensor_list <- list.files(pattern="*.csv")#creating a list of sensor files
WD <- getwd()#get working directory to combine files
SD <- sensor_list %>% map_dfr(read_csv,.id = "WD") %>% group_by(WD) %>% mutate(id=cur_group_id()) %>% filter(time<=60) #combine all files and filter anything under a minute or 60s
SD1 <- SD %>% summarise(wx=mad(wx),wy=mad(wy),wz=mad(wz)) %>% ungroup()
SD2 <- SD1 %>% select(-1)
```

##PCA for jumping data
```{r}

PCA <- prcomp(SD2, scale.=TRUE)# run PCA
summary(PCA)#get cumulative Proportion
PCA$rotation #Understand what each component is made up
SD3 <- augment(PCA,data=SD2) #create a frame with all the information 
biplot(PCA)
plot(PCA,type="lines")
#From the biplot and the scree plot it makes sense to remove the 3rd components as PC1 and 2 account for more than 99% of the variance. 
```

##K-means
```{r}

KT <- SD3 %>% select(5:6)
Kmeans <- kmeans(KT, 3)
Clust <- augment(Kmeans,KT)
p1 <- 
  ggplot(Clust, aes(x =.fittedPC1 , y =.fittedPC2)) +
  geom_point(aes(color = .cluster), alpha = 0.8, size=1.5*(SD1$wx))+
  labs(x="Move Up/Down & Left/Right",y="Move Front/Back",title = "Movement of Jumping")
p1 #basically beautifying the biplot

## Since both our x and y axis measure the movement of jumping, group members in the cluster that is colser to point (0,0) would be experts; person in cluster that far away from (0,0) would be novice. 
```

##Measure correlation to outcome (# of jumps in one minute)
```{r}
Outcomes <- read_excel("Assignment  6 Outcome data.xlsx")
T2O <- augment(Kmeans,Outcomes)
T2O$.cluster=as.numeric(T2O$.cluster)
ggcorr(T2O[,-1:-2,], method = c("everything", "pearson"))
cor <- cor(T2O[,-1:-2,], method = "pearson" )
cor
#There seems to be a moderate correlation (-.58) between the clusters and the number of number of jumps. 
```


#Task III
- Devise five questions on a five point Likert scale that ask members of your group about their experience with your chosen task
- Collect data from all members of your group
- Run a PCA analysis on the data
- What does PC1 represent in your analysis?
- Visualize the PC1 results for each member of your group
##Libraries
```{r}
library(ggplot2)
library(GGally)
library(factoextra)
library(dplyr)
```

##Data import
```{r}
S1 = read.csv("surveydata.csv", header = T)
```

##Visualize correlations
```{r}
ggpairs(S1, 2:6, progress = FALSE)
ggcorr(S1[,-1], method = c("everything", "pearson"))
```

##PCA
```{r}
drop <- c("Name")
S2 <- S1[,!(names(S1) %in% drop)]
pcas <- prcomp(S2, scale. = TRUE)

pcas$sdev

#To convert this into variance accounted for we can square it, these numbers are proportional to the eigenvalue

pcas$sdev^2

#A summary of our pca will give us the proportion of variance accounted for by each component

summary(pcas)

#We can look at this to get an idea of which components we should keep and which we should drop

plot(pcas, type = "lines",ylim=c(0,3))


pcas$rotation

loadings <- abs(pcas$rotation) #abs() will make all eigenvectors positive

head(summary(pcas))

V1 = pcas$x
V2 <- V1
rownames(V2)<-S1$Name
V3 <- as.data.frame(V2)
names <- c("Sara","Yuan","Yurui","Jingshu","Jie","Shuyi","Manrui","Xingyi")
barplot(V3$PC1, ylab = "Each member's score on PC1", ylim=c(-4,4), names.arg=names, cex.names=1)
```

##What PC1 represents

PC1
Q1..How.comfortable.your.feel.jumping...1...not.comfortable.at.all..5...very.comfortable.                                                                                0.52902674
Q2.How.often.you.add.jumps.to.your.workout...1.not.at.all..5..very.frequent.                                                                                             0.30168028
Q3..How.tired.you.felt.after.jumping...1.very.tired..5..not.tired.at.all.                                                                                               -0.01970875
Q4..Do.you.think.you.are.in.good.physical.shape....1.I.am.an.expert.couch.potato...5..I.can.run.a.marathon.tomorrow.                                                     0.56383739
Q5..How.often.do.you.exercise...5.almost.every.day..4.once.or.twice.a.week..3.once.or.twice.a.month..2.once.or.twice.three.months..1.once.or.twice.half.a.year.or.less.  0.55751114

##Answer: According to the eigenvectors above, PC1 = 0.529*Q1 + 0.302*Q2 + (-0.020)*Q3 + 0.564*Q4 + 0.558*Q5. In particular, question 1, 2, 3, and 5 have a weight of at least +/- 0.25, which is a noticeable contribution to this principal component. Based on the what those four questions ask, PC1 can be considered a construct of "body-training management and preference to jumping activities". 



#Task IV

##Q:If you could only choose one thing to predict the score for each member of your group (raw data variable, a cluster or a PC) what would it be and why?

##Answer: We would like to choose cluster as an indicator to predict the score of jumping rope. By observing the number of jumps for different clusters in T2O, we could find that people in cluster3 have better performance on average. According to p2 we could figure out that group members in cluster 3 have least movement. So, there is an inverse relationship bwtween number of jumps and movements during jumping, and it's safe to make a conclusion that in order to jump more in the limited time, expert would keep the least level of movements to save both energy and time. Therefore, we would like to assign higher scores for group members in cluster 3. On the other side, members in cluster 1 and 3 have relative larger movement, so we will assign lower scores for them. 

## Our advice would be that try to make limited movements in left to right and front to back during your jumps. Don't jump too high and try to jump in the same place.You cna do this by marking and X on the floor with take and ensruring you stay within the bounds of the X.

```{r}
p2 <- ggplot(Clust, aes(x =.fittedPC1 , y =.fittedPC2)) +
  geom_point(aes(color = .cluster), alpha = 0.8, size=1.5*(SD1$wx)) +
  labs(x="Move Up/Down & Left/Right",y="Move Front/Back",title = "Movement of Jumping")
p2
jumps <- Task2_outcomes$Jumps
p3 <- ggplot(data = Task2_outcomes, aes(Name,Jumps)) +geom_point(aes(color = .cluster), alpha = 0.8,pch=3,cex=4)
p3
```
